The Iterative Signature Algorithm for Gene Expression Data

### 2010-04-12 eisa/inst/doc/EISA_tutorial.Rnw
eisa: tutorials use 'xlib' graphics, if available.

<<set width,echo=FALSE,print=FALSE>>=
options(width=60)
options(continue=" ")
@

@@

Profile plots visualize the difference between the genes (or samples)
in the modules and the rest of the expression data. A profile plot
contains a line plot for every single gene (or sample) and the genes
that belong to the module have a different color, see
Fig.~\ref{fig:parallel}.
<<parallel.pre,echo=FALSE,results=hide>>=
if (require(Cairo)) {
  CairoPNG("plot-parallel.png", 400, 400 )
} else {
  png("plot-parallel.png", 400, 400 )
}
@ 
<<parallel>>=
profilePlot(modules, 2, ALL, plot="both")
@
<<parallel.post,echo=FALSE,results=hide>>=
dev.off()
@ 
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{plot-parallel.png}
\caption{Profile plots for the second bicluster found by ISA.}
\label{fig:parallel}
\end{figure}

>>>>

<<set width,echo=FALSE,print=FALSE>>=
options(width=60)
options(continue=" ")
try(X11.options(type="xlib"), silent=TRUE)
@

@@

Profile plots visualize the difference between the genes (or samples)
in the modules and the rest of the expression data. A profile plot
contains a line plot for every single gene (or sample) and the genes
that belong to the module have a different color, see
Fig.~\ref{fig:parallel}.
<<parallel.pre,echo=FALSE,results=hide>>=
png("plot-parallel.png", 400, 400 )
@ 
<<parallel>>=
profilePlot(modules, 2, ALL, plot="both")
@
<<parallel.post,echo=FALSE,results=hide>>=
dev.off()
@ 
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{plot-parallel.png}
\caption{Profile plots for the second bicluster found by ISA.}
\label{fig:parallel}
\end{figure}
